Twists of supersymmetric gauge theories

### 2020-01-13 paper.tex
(0,N)

\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts on the left by the adjoint action. 
\end{thm}
\begin{proof}
First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$ and  $\int (\phi, \psi_0^*)$.  
Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
which can be integrated out using Proposition \ref{prop:BRSTdoublet}.

>>>>

\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The minimal twist of 2d $\cN=(0,\cN_-)$ super Yang-Mills with Lie algebra $\fg$ is $U(1)$-equivariantly equivalent to holomorphic $BF$ theory on $\CC$ for the Lie algebra $\fg$ coupled to a free fermion system on $\CC$ with values in the representation $\fg \otimes W_-' \cong \fg \otimes \CC^{\cN_- - 2}$ where $\fg$ acts by the adjoint action. 
\end{thm}
\begin{proof}
First, we integrate out the fields $\lambda_{0}$ and $\lambda_{1,1}^*$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{1,0}^*)$.  
Thus, the pair $(\lambda_{1,0}, A_{1,0})$ forms a BRST doublet, 
which can be integrated out using Proposition \ref{prop:BRSTdoublet}.
